Predator summary

### 2023-01-25 reports/01_predators.qmd
rasterized predator counts

>>>>

### Maps

```{r}
#| label: snpt_map
#| warning: false

snpt_sf <- predators_agg %>% 
  filter(species == "SNPT",
         year == 2016) %>% 
  sf::st_as_sf(coords = c("lon_mean", "lat_mean"), 
               crs = sp::CRS("+proj=longlat +datum=WGS84"))

snpt_stars <- rasterize_counts(snpt_sf, res = 1e4, layer_name = "SNPT")

map_lim <- sf::st_bbox(snpt_sf) %>% 
  sf::st_as_sfc(crs = "EPSG:4326") %>% 
  sf::st_transform(sg_proj()) %>% 
  sf::st_bbox()

ggplot() +
  geom_sf(data = sg_sf) +
  stars::geom_stars(aes(fill = SNPT), data = snpt_stars) +
  scale_fill_gradient(low = "lightblue", high = "darkred",
                      na.value = NA) +
  expand_limits(fill = 0) +
  coord_sf(xlim = map_lim[c("xmin", "xmax")],
           ylim = map_lim[c("ymin", "ymax")],
           expand = FALSE,
           crs = sg_proj()) +
  theme_minimal() +
  theme(axis.title = element_blank())

```
